---
title: "Age and gender in the 2021 US GSS"
subtitle: "Possible selection effect in ages 18-35"
author: 
  - Rohan Alexander
thanks: "Code and data are available at: https://github.com/RohanAlexander/gss_analysis."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
```

# Introduction

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point). 

@citeR


# Data

Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it. 



# Results


# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Supplementary survey

Our supplementary survey is available here: LINK

## Preamble

The purpose of this survey is to further investigate gender. We are interested in more detailed gender data than is provided by the main US GSS and will use this to guide the development of submissions to change future iterations of the GSS.

By proceeding with the survey, you understand that we will use your responses to better understand gender responses in the GSS. The survey is voluntary, and if you decide to participate you can skip questions and withdraw at any time.

## Questions

1. What is your age?
    - 18-29
    - ... ADD all the others
2. What is your gender?
    - Female
    - Male
    - Transgender
    - Non-binary
    - Genderqueer
    - Two-spirit
    - Other
ADD some other questions

## End page

Thank you very much for partiicpating in our survey. If you have any questions, you can email rohan.alexander@utoronto.ca






\newpage


# References


